DNA meth and IVF

### 2023-12-19 figs/art_example.Rmd
better example

det <- mres$detailed_sets$REACTOME_SENSORY_PERCEPTION

@@

filled.contour(k, color.palette = palette, xlim=c(XMIN,XMAX), ylim=c(YMIN,YMAX),
      plot.title = {
        abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
        title(main = "Reactome sensory perception", xlab = X_AXIS,
        ylab = Y_AXIS)
    })

pdf("fig7d.pdf")
filled.contour(k, color.palette = palette, xlim=c(XMIN,XMAX), ylim=c(YMIN,YMAX),
      plot.title = {
        abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
        title(main = "Reactome sensory perception", xlab = X_AXIS,
        ylab = Y_AXIS)
    })
dev.off()

>>>>

det <- mres$detailed_sets$REACTOME_NGF_STIMULATED_TRANSCRIPTION

@@

filled.contour(k, color.palette = palette, xlim=c(XMIN,XMAX), ylim=c(YMIN,YMAX),
      plot.title = {
        abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
        title(main = "Reactome NGF-stimulated transcription", xlab = X_AXIS,
        ylab = Y_AXIS)
    })

pdf("fig7d.pdf")
filled.contour(k, color.palette = palette, xlim=c(XMIN,XMAX), ylim=c(YMIN,YMAX),
      plot.title = {
        abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
        title(main = "Reactome NGF-stimulated transcription", xlab = X_AXIS,
        ylab = Y_AXIS)
    })
dev.off()
